Augraphy: A Data Augmentation Library for Document Images

### 2023-04-29 paper.tex
Cuts and reorganization of text to get down to 15 pages

The introduction of noise-like corruptions and other modifications to image data can be used as a way of estimating and evaluating model robustness.
Prior work in this space includes the use of image blurring, contrast and brightness changes, color alterations, partial occlusions, geometric transformations, pixel-level noise (e.g., salt-and-pepper noise, impulse noise, etc.), and compression artefacts (e.g., JPEG) to evaluate image classification and object detection models (e.g., \cite{image-quality-impact,imagenet-c,pathology-recommendations,Hosseini2017-kn-google-api,face-recognition-impact,pathology-schomig,Vasiljevic2016-al-bluring-impact}).
More specific to the document understanding field, recent prior work has used basic noise-like corruptions to evaluate the robustness of document classifiers trained on RVL-CDIP \cite{saifullah-2022}.
Our paper also uses robustness testing as a way to showcase the effectiveness of \emph{Augraphy}, but rather than general image modifications like those described above, we use document-centric modifications to produce human-readable distortions which challenge OCR models.

\section{Document Distortion, Theory \& Technique}
Many approaches exist for adding features to an image, and many types of features can be generated. The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.

These types of feature are certainly useful in general image analysis and understanding, but bear little relation to the types of features commonly found in real-world documents.

@@

\section{Augraphy}
This section dives into detail about the \emph{Augraphy} library.
We first provide a high-level overview of the library, then discuss the various augmentations supported out-of-the-box, and finally discuss details of the structure of the library.

\subsection{Overview}

@@

Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.

@@

\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post.
The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time --- and transform them prior to ``printing".

@@

\subsection{The Library}
\emph{Augraphy} is a Python-based library, allowing for maximal accessibility for practitioners, and is designed with an object-oriented structure, with concerns divided across a class hierarchy.
When composed, augmentations from the library interact to produce complex document image transformations, generating realistic new synthetically-augmented document images.

There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality:

@@

The value added by the \texttt{AugraphyPipeline} class over a bare list of functions applied in sequence to an image is principally in the collection of runtime metadata; the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation.
 This pipeline metadata allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features, facilitating (re)production of documents as in Figure \ref{fig:intro}.

>>>>

Testing a model's robustness with challenging datasets is a vital step to evaluate a model's resilience against real-world scenarios, helping developers identify and address weaknesses for enhanced effectiveness in document processing tasks.

Prior work for evaluating image classification and object detection models includes image blur; contrast, brightness and color alterations; masking; geometric transforms; pixel-level noise; and JPEG compression artefacts (e.g., \cite{image-quality-impact,imagenet-c,pathology-recommendations,Hosseini2017-kn-google-api,face-recognition-impact,pathology-schomig,Vasiljevic2016-al-bluring-impact}).
More specific to the document understanding field, recent prior work has used basic noise-like corruptions to evaluate the robustness of document classifiers trained on RVL-CDIP \cite{saifullah-2022}.
Our paper also uses robustness testing as a way to showcase the effectiveness of \emph{Augraphy}, using specialized document-centric alterations to produce human-readable distortions which challenge OCR and face-detection models.

\section{Document Distortion, Theory \& Technique}
As referenced in the \emph{Related Work} section of this paper, many general-purpose image distortion techniques exist for data augmentation and robustness testing.  While these techniques are useful in general image analysis and understanding, they bear little resemblance to the features commonly found in real-world documents.

@@

\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into \emph{three phases}: \textbf{ink}, \textbf{paper}, and \textbf{post}.
The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time --- and transform them prior to ``printing".

\section{Augraphy}

@@

@@

@@

\subsection{The Library}
There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality that when composed generate realistic synthetically-augmented document images:

@@
